Assigning Scouts to Optimal Patrols

### 2016-05-25 draft1.tex
Adding Previous of Work section
Still have to add actual text. Only outline is there.

@@

\section*{Appendix B}
The solution for finding the Stirling number of the second kinds for $n = 13$ scouts to be arranged in $k = 2$ troops:
\begin{gather*}
	S(n,k) = \frac{1}{k!} \sum_{i=0}^{k}(-1)^k {2 \choose i} (k - i)^{n} \\
	S(13,2) = \frac{1}{2!} \sum_{i=0}^{2}(-1)^2 {2 \choose i} (2 - i)^{13} \\
	S(13, 2) = 4095
\end{gather*}

>>>>

\section*{Previous Work}
(Currently reading more on Max Flow-Min cut, K-means clustering, Graph clustering: http://www.sciencedirect.com/science/article/pii/S1574013707000020. We will talk about generating random solutions)

@@

\section*{Appendix B}
The solution for finding the Stirling number of the second kind for $n = 13$ scouts to be arranged in $k = 2$ troops:
\begin{gather*}
	S(n,k) = \frac{1}{k!} \sum_{i=0}^{k}(-1)^k {2 \choose i} (k - i)^{n} \\
	S(13,2) = \frac{1}{2!} \sum_{i=0}^{2}(-1)^2 {2 \choose i} (2 - i)^{13} \\
	S(13, 2) = 4095
\end{gather*}
